Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-07-12 final/introduction.tex
5 values -> 4 values

Next, we show that checking whether an execution violates this ``local'' property for a value $x$ can be done using a class of register automata~\cite{DBLP:journals/tcs/KaminskiF94,DBLP:conf/icalp/Cerans94,DBLP:conf/stacs/SegoufinT11} (transition systems where the states consist of a fixed set of registers that can receive values and be compared). Actually, only two registers are needed: one register $r_1$ for storing a priority guessed at the initial state, and one register $r_2$ for reading priorities as they occur in the execution and comparing them with the one stored in $r_1$. We show that registers storing values added to or removed from the priority queue are not needed, since any data-independent implementation admits a violation to linearizability whenever it admits a violation where the number of values is constant, and at most 5 (the number of priorities can still be unbounded).

>>>>

Next, we show that checking whether an execution violates this ``local'' property for a value $x$ can be done using a class of register automata~\cite{DBLP:journals/tcs/KaminskiF94,DBLP:conf/icalp/Cerans94,DBLP:conf/stacs/SegoufinT11} (transition systems where the states consist of a fixed set of registers that can receive values and be compared). Actually, only two registers are needed: one register $r_1$ for storing a priority guessed at the initial state, and one register $r_2$ for reading priorities as they occur in the execution and comparing them with the one stored in $r_1$. We show that registers storing values added to or removed from the priority queue are not needed, since any data-independent implementation admits a violation to linearizability whenever it admits a violation where the number of values is constant, and at most 4 (the number of priorities can still be unbounded).
